Homework 5: Constraint and Brokerage in the Florentine Wedding dataset

### 2022-03-24 _academics/ps753-hw5/ps753-hw5.Rmd
fix link

Building on [last week's look](../ps753-hw3/index.html) at basic network centrality attributes in the Florentine Wedding dataset, we're going to look at two new measurements of centrality: brokerage and constraints.

>>>>

Building on [last week's look](../ps753-hw4/index.html) at basic network centrality attributes in the Florentine Wedding dataset, we're going to look at two new measurements of centrality: brokerage and constraints.
